Methods for Large Scale Learning to Rank

### 2014-09-25 report/Chapters/Introduction.tex
thesis overview klopt weer

\begin{description}
\item[Chapter II: Background]{introduces the reader to the basic principles and recent work in the fields of Learning to Rank.}
\item[Chapter III: Related Work]{concisely describes existing work in the field of parallel Learning to Rank.}
\item[Chapter IV: Benchmark Results]{sketches the accuracy of existing Learning to Rank methods on several benchmark data sets and describes the selection of Learning to Rank methods for the parallelisation experiments.}
\item[Chapter V: Selected Learning to Rank Methods]{describes the algorithms and details of the Learning to Rank methods selected in Chapter IV.}
\item[Chapter VI: Implementation]{describes implementation details of the Learning to Rank algorithms in the Hadoop framework.}
\item[Chapter VII: Results \& Discussion]{presents and discusses speed-up results for the implemented Learning to Rank methods.}
\item[Chapter VIII: Conclusion]{summarizes the results and answers our research questions based on the results. The limitations of our research as well as future research directions in the field are mentioned here.}
\end{description}

>>>>

\begin{description}
\item[Chapter II: Background]{introduces the reader to the basic principles and recent work in the fields of Learning to Rank and the MapReduce computing model. Aims at bringing those unfamiliar with those topics up to speed to be able to understand the succeeding chapters of this thesis.}
\item[Chapter III: Related Work]{concisely describes existing work in the field of parallel and distributed Learning to Rank.}
\item[Chapter IV: Benchmark Data Sets]{described the characteristics of the existing benchmark data sets in the Learning to Rank field.}
\item[Chapter V: Cross Benchmark Comparison]{described the methodology of a comparison of ranking accuracy of Learning to Rank methods across benchmark data sets and described the results of this comparison.}
\item[Chapter VI: Selected Learning to Rank Methods]{describes the algorithms and details of the Learning to Rank methods selected in Chapter V.}
\item[Chapter VII: Implementation]{describes implementation details of the Learning to Rank algorithms in the Hadoop framework.}
\item[Chapter VIII: MapReduce Experiments]{presents and discusses speed-up results for the implemented Learning to Rank methods.}
\item[Chapter IX: Conclusions]{summarizes the results and answers our research questions based on the results. The limitations of our research as well as future research directions in the field are mentioned here.}
\item[Chapter X: Future Work]{describes several directions of research worthy follow-up research based on our findings.}
\end{description}
